### 2018-06-06 latex/sc18/introduction.tex

%The CP decomposition is a low-rank approximation of a multi-dimensional array, or tensor, which generalizes matrix approximations like the truncated singular value decomposition. 
%As in Figure \ref{fig:cpdecomposition}, CP decomposition approximates the given input matrix as sum of $k$ rank-1 tensors.  
The CP decomposition is a low-rank approximation of a multi-dimensional array, or tensor, which generalizes matrix approximations like the truncated singular value decomposition.
It approximates the input tensor by a sum of rank-one tensors, which are outer-products of vectors. 
CP is often used for finding hidden patterns, or latent factors, within tensor data, particularly when the goal is to interpret the factors, and it is popular within the signal processing, machine learning, and scientific computing communities.

@@

We summarize our main contributions as follows:
\begin{itemize}
		\item we present the first distributed-memory parallel implementation of NNCP algorithms for arbitrary-dimension dense tensors,
		\item we optimize the use of dimension trees for dense tensors, avoiding recomputation across multiple MTTKRPs,
		\item our parallel algorithm is communication optimal with a carefully chosen processor grid,
		\item we demonstrate a performance improvement of up to $2.2\times$ over the existing state-of-the-art parallel software on 3D tensors,
		\item our implementation obtains efficient parallel scaling of up to $253\times$ on $512$ cores.
\end{itemize}

>>>>

%The CP decomposition is a low-rank approximation of a multi-dimensional array, or tensor, which generalizes matrix approximations like the truncated singular value decomposition. 
%As in Figure \ref{fig:cpdecomposition}, CP decomposition approximates the given input matrix as sum of $k$ rank-1 tensors.  
The CP decomposition is a low-rank approximation of a multi-dimensional array, or tensor, which generalizes matrix approximations like the truncated singular value decomposition.
\textcolor{red}{It approximates the input tensor by a sum of rank-one tensors, which are outer products of vectors. }
CP is often used for finding hidden patterns, or latent factors, within tensor data, particularly when the goal is to interpret the factors, and it is popular within the signal processing, machine learning, and scientific computing communities.

@@

\red{We summarize our main contributions as follows:
\begin{itemize}
		\item we present the first distributed-memory parallel implementation of NNCP algorithms for arbitrary-dimension dense tensors,
		\item we optimize the use of dimension trees for dense tensors, avoiding recomputation across multiple MTTKRPs,
		\item our parallel algorithm is communication optimal with a carefully chosen processor grid,
		\item we demonstrate a performance improvement of up to $2.2\times$ over the existing state-of-the-art parallel software on 3D tensors,
		\item our implementation obtains efficient parallel scaling of up to $1771\times$ on 4096 cores.
\end{itemize}}
